What is happening on Twitter? A framework for student research projects with tweets

### 2020-09-06 Rmd/jse-special-issue-2020-october.Rmd
added taskSCheduleR note

Readers may need to slightly amend the above line to conform to requirements of their operating system's `crontab`.

>>>>

Mac users may need to slightly amend the above line to conform to requirements of their operating system's `crontab`. Windows users may want to schedule task with the R package `taskscheduleR`, which interacts with the Windows task scheduler.
